Exploring probability distributions for bivariate temporal granularities

### 2019-12-02 main.Rmd
acyclic time granularities def

Periodic and Quasi-periodic behavior can be defined by a repeating pattern, except for a finite number of granules that can be seen as discontinuity points in the granularity in case of quasi-periodic behavior. Aperiodic time granularities are the ones which can not be specified as a periodic repetition of a pattern of granules. Most public and school holidays repeat every year, but there is no period within which their behavior remains constant. For example, U.S labour day is the first Monday in September and U.S. Memorial Day is the last day in May. A classic example can be that of Easter. 
Examples of aperiodic granularity can also be an event that covers the first and third Monday of the month between June and October, except for state holidays. All of these are still recurring events, but recurring with non-periodic patterns. As such, plausible $k_i$ from \autoref{tab:aperiodic} can be infinite for aperiodic granularities.

>>>>

Periodic and Quasi-periodic behavior can be defined by a repeating pattern, except for a finite number of granules that can be seen as discontinuity points in the granularity in case of quasi-periodic behavior. Aperiodic time granularities are the ones which can not be specified as a periodic repetition of a pattern of granules. Most public holidays repeat every year, but there is no period within which their behavior remains constant. For example, U.S labour day is the first Monday in September and U.S. Memorial Day is the last day in May. A classic example can be that of Easter, whose dates repeat only after 5,700,000 years. Examples of aperiodic granularity may also include school holidays or a scheduling event that covers the first and third Monday of the month between June and October, except for state holidays. All of these are still recurring events, but recurring with non-periodic patterns. As such, plausible $k_i$ from \autoref{tab:aperiodic} can be infinite for aperiodic granularities.
